% Final results refinement snippet for paper integration

\subsection{Final Full Multi-Seed Comparison}
The final comparison was performed on the two dataset variants, \texttt{v3\_1\_fixed} and \texttt{v3\_2\_combatfix}, using full replay-aware seeds $42,43,44$ for the two main tabular finalists: Random Forest (RF) and XGBoost (XGB). RF was evaluated with its best profile, \texttt{no\_counter}, while XGB was evaluated with the full feature set.

\begin{table}[h]
\centering
\caption{Final full multi-seed results. Mean $\pm$ standard deviation over seeds 42, 43, and 44.}
\begin{tabular}{l l l c c c c}
\hline
Dataset & Model & Profile & Accuracy & Bal. Acc. & ROC-AUC & Log Loss \\
\hline
v3\_1\_fixed & RF  & no\_counter & 0.6133 $\pm$ 0.0055 & 0.6111 $\pm$ 0.0051 & 0.6605 $\pm$ 0.0055 & 0.6503 $\pm$ 0.0023 \\
v3\_1\_fixed & XGB & full        & 0.6128 $\pm$ 0.0054 & 0.6093 $\pm$ 0.0049 & 0.6601 $\pm$ 0.0048 & 0.6484 $\pm$ 0.0025 \\
v3\_2\_combatfix & RF  & no\_counter & 0.6128 $\pm$ 0.0052 & 0.6107 $\pm$ 0.0048 & 0.6603 $\pm$ 0.0057 & 0.6504 $\pm$ 0.0024 \\
v3\_2\_combatfix & XGB & full        & 0.6128 $\pm$ 0.0069 & 0.6093 $\pm$ 0.0062 & 0.6597 $\pm$ 0.0059 & 0.6486 $\pm$ 0.0030 \\
\hline
\end{tabular}
\end{table}

These results show that \texttt{v3\_1\_fixed} is at least as strong as \texttt{v3\_2\_combatfix} in the final regime. The earlier staged indication that \texttt{v3\_2\_combatfix} might dominate is not confirmed by the final full multi-seed comparison. At project end-state, RF and XGB are effectively tied: RF is marginally stronger on classification-oriented metrics, while XGB is marginally stronger on log loss.

\subsection{Deep Challenger}
The final deep-learning challenger was evaluated on full \texttt{v3\_1\_fixed} with validation-based candidate selection.

\begin{table}[h]
\centering
\caption{Final deep challenger result on full \texttt{v3\_1\_fixed}.}
\begin{tabular}{l l c c c c}
\hline
Dataset & Model & Accuracy & Bal. Acc. & ROC-AUC & Log Loss \\
\hline
v3\_1\_fixed & Deep finalist & 0.6093 $\pm$ 0.0051 & 0.6083 $\pm$ 0.0042 & 0.6581 $\pm$ 0.0041 & 0.6506 $\pm$ 0.0025 \\
\hline
\end{tabular}
\end{table}

The deep model is competitive but remains slightly below both tabular finalists. It should therefore be presented as a credible challenger rather than the final winner.

\subsection{Rigorous Calibration}
Calibration was performed rigorously by fitting post-hoc calibrators on validation predictions and evaluating them on test predictions. RF benefits from post-hoc calibration, whereas XGB is already well calibrated in its uncalibrated form and does not obtain meaningful gains from Platt or isotonic calibration.

\subsection{Final Recommendations}
If the priority is classification, the recommended final model is \textbf{RF + \texttt{v3\_1\_fixed} + \texttt{no\_counter}}. If the priority is probability quality, the recommended final model is \textbf{XGB + \texttt{v3\_1\_fixed} + full features}.
